\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
	\vspace*{-9pt}
	\begin{verse}
		\textbf{#1}   #2
	\end{verse} 
}

\newcommand{\lineunder} {
	\vspace*{-8pt} \\
	\hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
	{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} 
	\vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
	{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
	\vspace*{-8pt}
	\begin{center}
		{\LARGE \scshape {#1}}\\
		#2 \\	#3
	\end{center}
	\vspace*{-8pt}
}

\newenvironment{achievements}{
	\begin{list}
		{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
	\end{list}
}

\newcommand{\schoolwithcourses} [4] {
	 \textbf{#1} #2 $\bullet$ #3\\ 
	#4 \\
	\vspace*{5pt}
}

\newcommand{\school} [4] {
	 \textbf{#1} #2 $\bullet$ #3\\ 
	#4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%\small
%\smallskip
\vspace*{-36pt}

\contact{Robert G. Cofield}
{257 South Gay Street, Apt 317A, Auburn AL 36830}
{(205) 260-7269 $\bullet$ robertgcofield@gmail.com}


%%%%%%%%%%%%%%%%%%
%% Work History %%
%%%%%%%%%%%%%%%%%%

\header{Work History}

	%% GAVLab %%
	\employer{GPS and Vehicle Dynamics Laboratory} {May 2012 - Present}
	{Assistant Researcher}
		
		\begin{achievements}
			% MOOS/ROS Bridge - FHWA2
			\item Designed and implemented data bridge between two message passing architectures for flexible, robust error calculation and visualization of multiply derived position solutions. Optimized algorithm through real-time testing in instrumented vehicle.
			% FHWA2 GUI
			\item Created graphical user interface to aid in the development of navigation sensor fusion algorithms, allowing user to visualize positioning solutions and error ellipses for real-time comparison.
			% MARV
			\item Trained coworkers in lightweight robotic operating systems while programming way point identification capabilities using point clouds for a miniature autonomous ground vehicle.
			% FHWA3
			\item Currently investigating sensor fusion algorithms for providing navigation information to blind pedestrians, incorporating map database information, limited GNSS coverage, stereo camera data, and multiple IMU devices.
		\end{achievements}

	%% Fargason - Construction %%
	\employer{Fargason Contracting, Inc} {May 2009 - January 2010}
	{Assistant to Licensed Contractor and Electrician}
		
		\begin{achievements}
			\item Trained in operating and maintaining an extensive array of heavy machinery and power tools.
			\item Learned equipment and chemical safety procedures in both industrial and residential settings.
		\end{achievements}


%%%%%%%%%%%%%%%
%% Education %%
%%%%%%%%%%%%%%%

\header{Education}

	%% Undergraduate %%
	\schoolwithcourses{Auburn University}
	{Auburn, AL, USA } { Bachelor of Science in Mechanical Eng., May 2013}
	{Cumulative GPA: $3.58/4.00$}
		
		\area{Mechanical Engineering}
			{ CAD $\cdot$ Modeling and Control of Dynamical Systems $\cdot$ FEA $\cdot $ Mechatronics $\cdot$ Mechanics of Materials $\cdot$ Machining $\cdot$ Microcontroller Programming $\cdot$ Signal Conditioning and Processing $\cdot$ Sensor Calibration $\cdot$ Multivariable Calculus $\cdot$ Linear Algebra $\cdot$ Numerical Analysis $\cdot$ Dynamic Modeling $\cdot$ System Identification and Characterization}
		\area{Undergraduate Honors Thesis}
			{ Created an efficient graphical user interface to aid ground vehicle drivers in path fidelity and collision avoidance during low-visibility caravan scenarios. Used differential GPS techniques to implement relative positioning in real-time. Devised human testing scenarios to evaluate effectiveness.}
		
		\begin{achievements}
			\item Investigated robotic leg mechanism design for honors contract course credit. Modeled kinematics and dynamics of twelve-bar Jansen linkage to evaluate load transportation potential.
			\item Continued development of teamwork skills throughout numerous successful group projects.
			\item Honed communication skills during course in public speaking.
			\item Extended metal working experience during machine shop certification.
		\end{achievements}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Miscellaneous Abilities %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\header{Skills and Relevant Experience}

	\begin{achievements}
		\item C++, Python, MATLAB, Linux Shell, \LaTeX
		\item ROS, MOOS,  Solid Edge, ANSYS
		\item Repaired and tuned a cluth-actuated, rear wheel differential drive steering system on commercial mower with trailer dynamics, drawing on experience with zero-point-turn vehicle behavior.
		\item Completed CITI training to participate in IRB-approved human testing projects
	\end{achievements}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Miscellaneous Acheivements %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\header{Selected Honors and Memberships}

	\begin{achievements}
		\item Spirit of Auburn Founder's Scholarship
		\item ConocoPhillips Mechanical Engineering Scholarship
		\item Dean's List, Fall 2009 - Summer 2011
		\item Tau Beta Pi Engineering Honor Society
		\item Pi Tau Sigma Mechanical Engineering Honor Society
		\item Auburn University Linux Club
	\end{achievements}


\end{document}
